Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-08-01 main.tex

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
\caption{\textbf{AE: relabel y axis with [O/H] - [O/H]$_CNM$}The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
%mm
    time 
within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
\label{fig:stars}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
\caption{\textbf{Clarify vertical axis label} The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
%mm
    time 
within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
\label{fig:stars}
\end{figure}
